\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

% Remove page numbers
\pagestyle{empty}

% No paragraph indentation
\setlength{\parindent}{0pt}

% Bullet spacing optimized for resumes
\setlist[itemize]{
    leftmargin=15pt,
    topsep=2pt,
    itemsep=1pt,
    parsep=0pt
}

\begin{document}

% ==================== HEADER ====================
\begin{center}
    {\Large \textbf{PARSA SAMANDIZADEH SHOUSHTARI}}\\[3pt]
    Software Developer | AI-Native Full-Stack Engineering \\[6pt]
    604-861-8530 | \href{mailto:parsasamandizadeh@gmail.com}{parsasamandizadeh@gmail.com} | Burnaby, BC\\
    \href{https://parsasamandi.com}{parsasamandi.com} | \href{https://www.linkedin.com/in/parsa-samandi/}{linkedin.com/in/parsa-samandi} | \href{https://github.com/parsasamandi}{github.com/parsasamandi}
\end{center}

\vspace{5pt}

% ==================== TECHNICAL SKILLS ====================
\textbf{SKILLS}\\[4pt]

\textbf{Core Engineering:} PHP, Laravel, MySQL, REST APIs, RBAC, MVC Architecture, Relational Database Design, Git\\
\textbf{AI-Native Development:} Python, FastAPI, React, TypeScript, Next.js, Docker, RAG Pipelines, Semantic Search, FAISS, LLM APIs (OpenAI, Gemini)

\vspace{8pt}

% ==================== PROFESSIONAL EXPERIENCE ====================
\textbf{EXPERIENCE}\\[4pt]

\textbf{Lead Developer} \hfill Mar 2026 -- Present\\
Community Platform Development -- Greater Vancouver, BC\\
Bilingual Community Platform (Live: \href{https://www.rasoulallah.ca/}{rasoulallah.ca})
\begin{itemize}
    \item Architected and deployed a full-stack bilingual (English/Farsi) community platform using Laravel 12, Filament 3, and Laravel Octane with FrankenPHP; implemented CMS, membership, prayer times, events, and RBAC admin controls.
    \item Deployed via Docker on Railway with multi-environment R2 object storage and automated backups.
    \item \textbf{Stack:} Laravel 12, Filament 3, PHP, MySQL, Docker, Railway, AWS R2.
\end{itemize}

\vspace{4pt}

\textbf{Web Developer (Part-time, Volunteer)} \hfill Jan 2024 -- Present\\
Golestan Foundation -- Remote
\begin{itemize}
    \item Developed a scalable multi-user Laravel platform with admin dashboard and API layer, streamlining financial data management for 19 organizations.
    \item Engineered full-stack CRUD with secure authentication, granular RBAC, and normalized relational database design using PHP and MySQL.
    \item \textbf{Stack:} PHP, Laravel 8, MySQL, REST APIs, RBAC. \textbf{GitHub:} \href{https://github.com/parsasamandi/laravel-organization-dashboard-fa}{laravel-organization-dashboard-fa}
\end{itemize}

\vspace{4pt}

\textbf{Web Developer Intern} \hfill Mar 2020 -- Jan 2021\\
Almas Teb Rayan -- Tehran, Iran
\begin{itemize}
    \item Contributed to production Django and Laravel applications, gaining hands-on experience with web development workflows and database design.
    \item Collaborated with senior developers on query optimization, application architecture, and mentored pre-teen students in Java and Scratch programming.
    \item \textbf{Stack:} Python (Django), PHP (Laravel), MySQL, Java.
\end{itemize}

\vspace{5pt}

% ==================== SELECTED PROJECTS ====================
\textbf{SELECTED PROJECTS}\\[4pt]


\textbf{CoralSend} -- Open-source P2P file transfer contributor
\begin{itemize}
    \item Diagnosed and fixed large file download and file upload timestamp bugs in a WebRTC-based peer-to-peer file transfer application.
    \item \textbf{GitHub:} \href{https://github.com/twomodo/coralsend}{twomodo/coralsend}
\end{itemize}

\vspace{3pt}

\textbf{Semantic Search Engine} -- AI-powered vector search API
\begin{itemize}
    \item FastAPI service converting documents/queries into sentence embeddings and performing semantic similarity search via FAISS. Deployed on Railway.
    \item \textbf{Stack:} Python, FastAPI, FAISS, Sentence Transformers. \textbf{GitHub:} \href{https://github.com/parsasamandi/semantic-search-engine}{semantic-search-engine}
\end{itemize}

\vspace{3pt}

\textbf{PDF Chatbot} -- RAG-powered document Q\&A
\begin{itemize}
    \item RAG pipeline: chunk PDFs, embed chunks, retrieve relevant context, generate answers via LLM API.
    \item \textbf{Stack:} Python, LangChain, OpenAI, FAISS. \textbf{GitHub:} \href{https://github.com/parsasamandi/pdf-chatbot}{pdf-chatbot}
\end{itemize}

\vspace{5pt}

% ==================== EDUCATION ====================
\textbf{EDUCATION}\\[4pt]

\textbf{Diploma in Computer Science} \hfill 2023 -- 2025\\
Douglas College -- Burnaby, BC \\
Relevant Coursework: Data Structures \& Algorithms, Software Engineering, Computer Architecture, Object-Oriented Programming (C++)

\end{document}