\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}
\setlength{\parindent}{0pt}

\setlist[itemize]{
    leftmargin=15pt,
    topsep=2pt,
    itemsep=1pt,
    parsep=0pt
}

\begin{document}

% ==================== HEADER ====================
\begin{center}
    {\Large \textbf{PARSA SAMANDIZADEH SHOUSHTARI}}\\[3pt]
    AI-Native Software Developer | Applied AI and Full-Stack Development \\[6pt]
    604-861-8530 \,|\, \href{mailto:parsasamandizadeh@gmail.com}{parsasamandizadeh@gmail.com} \,|\, Burnaby, BC\\
    \href{https://parsasamandi.com}{parsasamandi.com} \,|\, 
    \href{https://www.linkedin.com/in/parsa-samandi/}{linkedin.com/in/parsa-samandi} \,|\, 
    \href{https://github.com/parsasamandi}{github.com/parsasamandi}
\end{center}

\vspace{4pt}

% ==================== PROFILE ====================
\textbf{PROFILE}\\[4pt]
Computer Science diploma graduate and AI-native software developer with hands-on experience building applied AI projects in retrieval-augmented generation (RAG), semantic search, and LLM-based document workflows. Background includes Python backend development, vector search pipelines, and full-stack web development through personal, volunteer, and internship experience. Seeking an applied AI internship where I can contribute to practical AI systems while continuing to grow under strong research and engineering mentorship.

\vspace{6pt}

% ==================== TECHNICAL SKILLS ====================
\textbf{TECHNICAL SKILLS}\\[4pt]
\textbf{Languages:} Python, PHP, JavaScript, TypeScript, SQL, Java, C++\\
\textbf{AI / ML:} RAG pipelines, semantic search, FAISS, sentence embeddings, LLM APIs, prompt design, document chunking and retrieval\\
\textbf{Frameworks / Tools:} FastAPI, Laravel, React, Next.js, Docker, Git, MySQL, REST APIs\\
\textbf{Other:} Relational database design, RBAC, MVC architecture, deployment workflows

\vspace{6pt}

% ==================== AI PROJECTS ====================
\textbf{AI PROJECTS}\\[4pt]

\textbf{Semantic Search Engine} \hfill Personal Project\\
\href{https://github.com/parsasamandi/semantic-search-engine}{github.com/parsasamandi/semantic-search-engine}
\begin{itemize}
    \item Built a FastAPI service for semantic document retrieval using sentence embeddings and FAISS vector search.
    \item Implemented a search workflow that retrieves documents by meaning rather than exact keyword matching.
    \item Deployed the project on Railway as a practical backend API for AI-powered search experimentation.
    \item \textbf{Stack:} Python, FastAPI, FAISS, Sentence Transformers, Railway
\end{itemize}

\vspace{3pt}

\textbf{PDF Chatbot} \hfill Personal Project\\
\href{https://github.com/parsasamandi/pdf-chatbot}{github.com/parsasamandi/pdf-chatbot}
\begin{itemize}
    \item Developed a local question-answering system for PDF documents using a retrieval-augmented generation pipeline.
    \item Processed documents into chunks, generated embeddings, retrieved relevant context, and passed the retrieved content to an LLM for answer generation.
    \item Explored practical trade-offs in document ingestion, retrieval quality, and response relevance.
    \item \textbf{Stack:} Python, LangChain, OpenAI API, FAISS
\end{itemize}

\vspace{3pt}

\textbf{LLM Learnings} \hfill Personal Study Repository\\
\href{https://github.com/parsasamandi/llm-learnings}{github.com/parsasamandi/llm-learnings}
\begin{itemize}
    \item Maintained a repository of structured experiments and notes covering LLM API usage, conversation memory, system prompts, structured outputs, and retrieval workflows.
    \item Used the project as a learning sandbox to strengthen understanding of applied LLM engineering concepts.
    \item \textbf{Focus Areas:} prompt engineering, memory patterns, structured responses, retrieval from documents
\end{itemize}

\vspace{6pt}

% ==================== EXPERIENCE ====================
\textbf{EXPERIENCE}\\[4pt]

\textbf{Lead Developer} \hfill Mar 2026 -- Present\\
Community Platform Development -- Greater Vancouver, BC\\
Live platform: \href{https://www.rasoulallah.ca/}{rasoulallah.ca}
\begin{itemize}
    \item Architected and deployed a bilingual community platform using Laravel 12, Filament 3, Laravel Octane, and FrankenPHP.
    \item Implemented content management, membership workflows, prayer times, events, and role-based admin controls.
    \item Deployed with Docker and configured object storage and backup workflows.
    \item \textbf{Stack:} Laravel, PHP, MySQL, Docker, Railway, AWS R2
\end{itemize}

\vspace{3pt}

\textbf{Web Developer (Part-time, Volunteer)} \hfill Jan 2024 -- Present\\
Golestan Foundation -- Remote
\begin{itemize}
    \item Developed a Laravel platform with admin dashboard and API functionality for multi-organization financial data management.
    \item Built CRUD workflows, authentication, RBAC features, and relational database structures for internal operations.
    \item \textbf{Stack:} PHP, Laravel 8, MySQL, REST APIs, RBAC\\
    \textbf{GitHub:} \href{https://github.com/parsasamandi/laravel-organization-dashboard-fa}{github.com/parsasamandi/laravel-organization-dashboard-fa}
\end{itemize}

\vspace{3pt}

\textbf{Web Developer Intern} \hfill Mar 2020 -- Jan 2021\\
Almas Teb Rayan -- Tehran, Iran
\begin{itemize}
    \item Contributed to Django and Laravel applications and gained early experience with backend development and database design.
    \item Supported senior developers with implementation tasks and query-related improvements.
    \item Also assisted in mentoring beginner students in Java and Scratch programming.
    \item \textbf{Stack:} Python, Django, PHP, Laravel, MySQL, Java
\end{itemize}

\vspace{6pt}

% ==================== OPEN SOURCE ====================
\textbf{OPEN-SOURCE CONTRIBUTION}\\[4pt]

\textbf{CoralSend} \hfill Contributor\\
\href{https://github.com/twomodo/coralsend}{github.com/twomodo/coralsend}
\begin{itemize}
    \item Contributed bug fixes to a peer-to-peer file transfer application.
    \item Worked on issues related to large file downloads and upload timestamp behavior.
\end{itemize}

\vspace{6pt}

% ==================== EDUCATION ====================
\textbf{EDUCATION}\\[4pt]

\textbf{Diploma in Computer Science} \hfill 2023 -- 2025\\
Douglas College -- Burnaby, BC\\
Relevant Coursework: Data Structures and Algorithms, Software Engineering, Computer Architecture, Object-Oriented Programming (C++)

\end{document}